---
title: "Reproducible Research: Peer Assessment 1"
output: 
html_document:
keep_md: true
---


## Loading and preprocessing the data

1. Load the data and explore the summary.
```{r}
repdata <- read.csv("activity.csv")
summary(repdata)
```

2. Convert data into a data.table. 
```{r}
library(data.table)
repdaily = as.data.table(repdata)
```

## What is mean total number of steps taken per day?

3. Calculate the total number of steps taken per day and assign to new data.frame.
```{r}
repdailysum <- repdaily[, lapply(.SD, sum), by = date]
repdailysum
```

4. Plotting a Histogram of the total steps taken per day
```{r}
hist(repdailysum$steps, ylim = c(0,30), xlim = c(0,25000), xlab = "Steps Taken Per Day", main = "Histogram of Total Steps Taken Per Day" )
```

5. Calculating the mean and median.
```{r}
meanstep <- format(mean(repdailysum$steps, na.rm = TRUE), digits=2, nsmall = 2)
medstep <- median(repdailysum$steps, na.rm = TRUE)
```
The mean and median of the total number of steps taken per day are `r meanstep` and `r medstep` respectively.

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?