---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

1. Load the data from zip file and explore the summary.
```{r}
unzip(zipfile = "activity.zip")
repdata <- read.csv("activity.csv")
dim(repdata)
str(repdata)
head(repdata)
summary(repdata)
```

2. Convert data into a data.table. 
```{r}
library(data.table)
repdaily = as.data.table(repdata)
```

## What is mean total number of steps taken per day?

3. Calculate the total number of steps taken per day and assign to new data.frame.
```{r}
repdailysum <- repdaily[, lapply(.SD, sum), by = date]
head(repdailysum)
```

4. Plotting a Histogram of the total steps taken per day
```{r}
hist(repdailysum$steps, ylim = c(0,12), xlim = c(0,25000), breaks = 20, xlab = "Steps Taken Per Day", main = "Histogram of Total Steps Taken Per Day" )
```

5. Calculating the mean and median.
```{r}
meanstep <- mean(repdailysum$steps, na.rm = TRUE)
medstep <- median(repdailysum$steps, na.rm = TRUE)
```
The mean and median of the total number of steps taken per day are `r round(meanstep, 0)` and `r medstep` respectively.

## What is the average daily activity pattern?
6. Using ggplot2 package to plot.
```{r}
library(ggplot2)
avgsteps <- aggregate(x=list(steps=repdata$steps), by=list(interval=repdata$interval),
                      FUN=mean, na.rm=TRUE)
ggplot(data=avgsteps, aes(x=interval, y=steps)) +
    geom_line() +
    xlab("5-minute Interval") +
    ylab("Average Number Of Steps Taken")
```

7. Find the 5-min interval with maximum number of steps.
```{r}
avgsteps[which.max(avgsteps$steps),]
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?